---
title: "In-class Exercise 09"
date: Mar 16, 2024
date-modified: "last-modified"
execute: 
  eval: true
  echo: true
  freeze: false
  message: false
  warning: false
---

# 1. Prepare the data

```{r}
pacman::p_load(igraph, tidygraph, ggraph, 
               visNetwork, lubridate, clock,
               tidyverse, graphlayouts)
```

```{r}
GAStech_nodes <- read_csv("data/GAStech_email_node.csv")
GAStech_edges <- read_csv("data/GAStech_email_edge-v2.csv")

```

```{r}
GAStech_edges <- GAStech_edges %>%
  mutate(SendDate = dmy(SentDate)) %>%
  mutate(Weekday = wday(SentDate,
                        label = TRUE,
                        abbr = FALSE))
```

```{r}
GAStech_edges_aggregated <- GAStech_edges %>%
  filter(MainSubject == "Work related") %>%
  group_by(source, target, Weekday) %>%
    summarise(Weight = n(), .groups = 'drop') %>%
  filter(source != target) %>%
  filter(Weight > 1) %>%
  ungroup()
```

# 2. Using `tbl_graph()` to build tidygraph data model.

In this section, you will use `tbl_graph()` of **tinygraph** package to build an tidygraph’s network graph data.frame.

Before typing the codes, you are recommended to review to reference guide of [`tbl_graph()`](https://tidygraph.data-imaginist.com/reference/tbl_graph.html)

```{r}
GAStech_graph <- tbl_graph(nodes = GAStech_nodes,
                           edges = GAStech_edges_aggregated, 
                           directed = TRUE)
```

```{r}
GAStech_graph
```

# 3. Plotting a basic network graph

```{r}
ggraph(GAStech_graph) +
  geom_edge_link() +
  geom_node_point()

```

# **4. Changing the default network graph theme**

In this section, you will use [*theme_graph()*](https://ggraph.data-imaginist.com/reference/theme_graph.html) to remove the x and y axes. Before your get started, it is advisable to read it’s reference guide at least once.

```{r}
g <- ggraph(GAStech_graph,
            layout='nicely') + 
  geom_edge_link(aes())+
  geom_node_point(aes(color=Department), size=3)
g + theme_graph()
```

```{r}
#| warning: false

set_graph_style()

g <- ggraph(GAStech_graph,
            layout='nicely') + 
  geom_edge_link(aes(width=Weight),
                 alpha=0.2) +
  scale_edge_width(range=c(0.1,5))+
  geom_node_point(aes(color=Department), 
                    size=3)
g + theme_graph()
```
```{r}
#| warning: false

set_graph_style()

g <- ggraph(GAStech_graph, 
            layout = "nicely") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = Department), 
                  size = 2)

g + facet_edges(~Weekday)

```

```{r}
#| warning: false
g <- GAStech_graph %>%
  mutate(betweenness_centrality = centrality_betweenness()) %>%
  ggraph(layout = "fr") + 
  geom_edge_link(aes(width=Weight), 
                 alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = Department,
            size=betweenness_centrality))
g + theme_graph()

```